Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-03-30 PAPER/main.tex
changed values in example of CPOP

For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,5\}, \{2,4\}, \{3,4\}, \{4,5\}\}$ and $\tau = 7$, one possible feasible solution is $\mathcal{T} = \langle(1,2), (5,4), (3,4), (4,2), (5,1) \rangle$.

>>>>

For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,6\}, \{2,3\}, \{3,5\}, \{4,4\}, \{4,5\}\}$ and $\tau = 7$, one possible feasible solution is $\mathcal{T} = \langle(1,2), (5,4), (4,4), (3,5), (3,2), (6,1) \rangle$.
